---
title: "s0-0_barseq_export"
author: "Kevin S. Blake"
date: "2023-12-14"
output: html_document
editor_options: 
  chunk_output_type: inline
---

### **General organization** ---------------------------------------------------

- Fig 1. Overview (timeline, mechanisms)
    - Supp Fig 1. Strains overview (tree, plasmid)
    - Supp Fig 2. qRT-PCR validation
- Fig 2. Mono-culture exps (heatmap, GR)
    - Supp Fig 3. More heatmaps
- Fig 3. Barseq schema + validation
- Fig 4. Competitions
    - Supp Fig 4. ALL-none + ALL-MIN
    - Supp Fig 5. mech specific plots
    - Supp Fig 6. minDES2
    - Supp Fig 7. MIC vs rel ab
- Fig 5. Transfer exps.


```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 

source("_common.R")
source("s1-1_timeline_phylo.R")
source("s1-3_MICs-GRs.R")
source("s2-1_barseq-validate.R")
source("s2-2_barseq-competitions.R")

```

### **Figure M01** Timeline Overview -------------------------------------------

```{r M01_export}

print(timeline_plot)

timeline.fname <- stringr::str_interp("${out.path}/${fln.prfx}-M01_timeline.pdf")
ggsave(timeline_plot, filename=timeline.fname, device=cairo_pdf, height=1.25, width=6)

```


### **Supp. Figure S01** Trees overview ----------------------------------------

```{r S01_export}

# Merge trees ----------------------------------------------------------------
p.trees.merge <- ggarrange(p2.EFF.tree, p2.RPP.tree, p2.DES_1.tree, p2.DES_2.tree, ncol=4, nrow=1)

print(p.trees.merge)

# Export individual trees
EFF.p2.fname <- stringr::str_interp("${out.path}/${fln.prfx}-S01_EFF-tree.pdf")
ggsave(p2.EFF.tree, filename = EFF.p2.fname, device=cairo_pdf, height=6.5)

RPP.p2.fname <- stringr::str_interp("${out.path}/${fln.prfx}-S01_RPP-tree.pdf")
ggsave(p2.RPP.tree , filename = RPP.p2.fname, device=cairo_pdf, height=3.2)

DES_1.p2.fname <- stringr::str_interp("${out.path}/${fln.prfx}-S01_DES1-tree.pdf")
ggsave(p2.DES_1.tree , filename = DES_1.p2.fname, device=cairo_pdf, height=3.8)

DES_2.p2.fname <- stringr::str_interp("${out.path}/${fln.prfx}-S01_DES2-tree.pdf")
ggsave(p2.DES_2.tree, filename = DES_2.p2.fname, device=cairo_pdf, height=3.8)


```


### **Figure M02** Monoculture fitness quantification --------------------------

```{r M02_export}

# GEN 1 & 2 & 3
ALL.heatmap.fname <- stringr::str_interp("${out.path}/${fln.prfx}-M02A_MIC-heatmap.pdf")    
p.MIC.ALL <- pheatmap(MIC.results.mat,
         color=colorRampPalette(c("#01353D", "#58B3C7","#B8FCFC"))(9),
         cluster_col=FALSE,
         annotation_row = annot.row,
         #cluster_rows = mat_cluster_rows,
         filename=ALL.heatmap.fname,
         annotation_colors=mech.pal2,
         cellheight=7.5, cellwidth=7.5,
         fontsize=6
         ) 

m02.merge <- ggarrange((ggarrange (p.strain.gr, p.mech.gr, nrow=2)), p.MICs.gr,  ncol=2)

print(m02.merge)

# fname.m02.merge <- stringr::str_interp("${out.path}/${fln.prfx}-M02_monoculture.pdf")
# ggsave(m02.merge, filename = fname.m02.merge, device=cairo_pdf, width=5.5, height=3) #width=5

# M02B 
fname.p.strain.gr <- stringr::str_interp("${out.path}/${fln.prfx}-M02B_strain-gr.pdf")
ggsave(p.strain.gr, filename = fname.p.strain.gr, device=cairo_pdf, width=2.25, height=1.7)

# M02C
mech.bin.fname <- stringr::str_interp("${out.path}/${fln.prfx}-M02C_mech-gr.pdf")
ggsave(p.mech.gr, filename = mech.bin.fname, device=cairo_pdf, width=2.25, height=1.7)

# M02D
fname.MIC.GR <- stringr::str_interp("${out.path}/${fln.prfx}-M02D_MIC-gr.pdf")
ggsave(p.MICs.gr, filename = fname.MIC.GR, device=cairo_pdf, width=2.9, height=3.9)


```

### **Supp. Figure S03** MIC dosage curves -------------------------------------

```{r S03_export}

print(p.MIC.dose)

export_plot(p.MIC.dose, fname="S03_MIC-dosage", w=10, h=10, fmt="pdf") 

```

### **Supp. Figure S04** More MIC heatmaps -------------------------------------

```{r S04_export}

# GEN 1 & 2
MIC.results.mat.1.2 <- subset(MIC.results.mat, select=-c(TIG, ERA, OMA))
ONE.TWO.heatmap.fname <- stringr::str_interp("${out.path}/${fln.prfx}-S04B_MIC-heatmap-gen1-2.pdf")

p.MIC.1.2 <- pheatmap(MIC.results.mat.1.2,
         color=colorRampPalette(c("#01353D", "#58B3C7", "#B8FCFC"))(9),
         #cluster_rows=FALSE,
         cluster_col=FALSE,
         #annotation_col = annot_col.df,
         annotation_row = annot.row,
         #cluster_rows = mat_cluster_rows,
         annotation_colors=mech.pal2,
         #legend=FALSE,
         filename=ONE.TWO.heatmap.fname,
         cellheight=12, cellwidth=12
         ) +
         theme_pub()

# GEN 1
MIC.results.mat.1 <- subset(MIC.results.mat.1.2, select=-c(DOX, MIN, MET))
ONE.heatmap.fname <- stringr::str_interp("${out.path}/${fln.prfx}-S04A_MIC-heatmap-gen1.pdf")

p.MIC.1.2 <- pheatmap(MIC.results.mat.1,
         cluster_col=FALSE,
         color=colorRampPalette(c("#01353D", "#58B3C7", "#B8FCFC"))(9),
         #annotation_col = annot_col.df,
         annotation_row = annot.row,
         #cluster_rows = mat_cluster_rows,
         annotation_colors=mech.pal2,
         filename=ONE.heatmap.fname,
         cellheight=12, cellwidth=12
         ) +
         theme_pub()
```

### **Figure M03:** Barseq validation

```{r M03_export}

# print(p02.val02.50k)
print(val02.rare.p02)

fname.val02.p02 <- stringr::str_interp("${out.path}/${fln.prfx}-M03_barseq-val.pdf")
ggsave(val02.rare.p02, filename = fname.val02.p02, device=cairo_pdf, width=4, height=3) #width=5

export_plot(p02.val02.50k.plot, fname="M03_barseq-validation_v2", w=1.5, h=1.5, fmt="pdf")  

```

### ***Figure M04:** ALL strain mix competitions -------------------------------

```{r M04_export}

# Merge + arrange
M04.merge <- ggarrange(p01.ALL.TET.EFF, p03.EFF.TET,
                       p01.ALL.DOX.RPP, p05.RPP.DOX,
                       p01.ALL.TIG.DES1, p02.DES1.TIG,
                       ncol=2, nrow=3)

print(M04.merge)

# Export
export_plot(M04.merge, fname="M04_competitions", w=6, h=6, fmt="pdf")  

```

### **Supp. Figure S05:** ALL-none + ALL-MIN ----------------------

```{r S05_export}

# Merge + arrange
S05.merge <- ggarrange(ggarrange(NA, NA, p00.ALL.none.merge, p00d.ALL.none.mech.bar, ncol=2, nrow=2),
                       p00c.ALL.none.gene.bar,
                       ggarrange(p01.ALL.MIN.RPP, ncol=2, nrow=2),
                       nrow=3
                       )
print(S05.merge)

export_plot(S05.merge, fname="S05_ALL-none", w=6, h=12, fmt="pdf")

```


### **Supp. Figure S06:** mech-specific mixes ----------------------------------

```{r S06_export}

# Merge + arrange
s06.mechspecmixes.merge <- ggarrange(p02.DES1.TET, p02.DES1.DOX, p02.DES1.MIN, p02.DES1.TIG,
                                     p03.EFF.TET, p03.EFF.DOX, p03.EFF.MIN, NA,
                                     p04.DES2.TET, p04.DES2.DOX, p04.DES2.MIN, NA,
                                     p05.RPP.TET, p05.RPP.DOX, p05.RPP.MIN, NA,
                                     # p01.minDES2.TET.EFF, p01.minDES2.DOX.RPP, NA, NA,
                                     # p01.minDES2.MIN.RPP, p01.minDES2.TIG.DES1, NA, NA,
                                     ncol=4, nrow=4)
print(s06.mechspecmixes.merge)

export_plot(s06.mechspecmixes.merge, fname="S06_moremixes", w=12, h=8, fmt="pdf") #w=12, h=12

```

### **Supp. Figure S07** minDES2 mix -------------------------------------------

```{r S07_export}

s07.mechspecmixes.merge <- ggarrange(p01.minDES2.TET.EFF, p01.minDES2.DOX.RPP, 
                                     p01.minDES2.MIN.RPP, p01.minDES2.TIG.DES1,
                                     ncol=2, nrow=2)
print(s07.mechspecmixes.merge)

export_plot(s07.mechspecmixes.merge, fname="S07_minDES2-mix", w=6, h=4, fmt="pdf") 

```

### **Supp. Figure S08:** MIC vs relab

```{r S08_export}

s08.merge <- ggarrange(p10.TET.MIC.relab, p10.DOX.MIC.relab, p10.MIN.MIC.relab, p10.TIG.MIC.relab)
print(s08.merge)

export_plot(s08.merge, fname="S08_ALL-relab-MIC", w=5, h=2.25, fmt="pdf")

```

### **Figure M05** Transfer experiments

```{r M05_export}

m05.transfer <- ggarrange(p50.TET.transf.01.merge, p51.TET.transf.02.merge,
                          p52.DOX.transf.01.merge, p53.DOX.transf.02.merge,
                          p54.TIG.transf.01.merge, p55.TIG.transf.01.merge,
                          ncol=2, nrow=3)
print(m05.transfer)

export_plot(m05.transfer, fname="M05_transfer", w=6, h=6.9, fmt="pdf") 
```
